My title

### 2023-03-24 outputs/paper/paper.qmd
changes in files and folder

```{r}
#| label: fig-presandeduc
#| fig-cap: Mother's and Father's Prestige Score
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8
#| fig-height: 4
#pres vs. educ
p1 <- ggplot(cleaned_data, aes(x=educ, y=papres10)) +
  geom_point(color="#69b3a2", size=2) +
  ggtitle("Father's Prestige Score vs Children's Education") +
  labs(x="Education (in Years)", y="Father's Prestige Score")+
  theme_bw()
p2 <- ggplot(cleaned_data, aes(x=educ, y=mapres10)) +
  geom_point(color="darkgreen",size=2) +
  ggtitle("Mother's Prestige Score vs Children's Education") +
  labs(x="Education (in Years)", y="Mother's Prestige Score")+
  theme_bw()

@@

ggplot(cleaned_data, aes(x = educ, fill = factor(born))) +
  geom_histogram(position = "dodge", binwidth = 1.5, alpha = 0.5, color = "black")+
   labs(title = "Education and Birthplace (if outside of US) for the Respondent",
       x = "Education (in Years)",
       y = "Count",
       fill = "Birthplace of the Respondent (if outside of US)")+
  theme_bw()
```

@@

```{r}
#| label: fig-maincome
#| fig-cap: Education vs Mother's Education with respect to Family Income
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8
#| fig-height: 4
ggplot(cleaned_data, aes(x = educ, y = maeduc, color = incom16)) +
  geom_jitter() +
  stat_smooth(method = "lm", se = FALSE) +
  facet_wrap(~incom16)+
  labs(title = "Education vs Mother's Education with respect to Family Income",
       x = "Education (in Years)",
       y = "Mother's Educaion (in Years)",
       color = "Family Income (at Age of 16)") +
  scale_color_discrete(name = "Family Income (at Age of 16)") +
  theme_bw()
```

@@

ggplot(cleaned_data, aes(x = educ, y = paeduc, color = incom16)) +
  geom_jitter() +
  stat_smooth(method = "lm", se = FALSE) +
  facet_wrap(~incom16)+
  labs(title = "Education vs Father's Education with respect to Family Income",
       x = "Education (in Years)",
       y = "Father's Educaion (in Years)",
  color = "Family Income (at Age of 16)") +
  scale_color_discrete(name = "Family Income (at Age of 16)") +
  theme_bw()
```

@@

# Model

>>>>

```{r}
#| label: fig-presandeduc
#| fig-cap: Mother's and Father's Prestige Score
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8
#| fig-height: 4
#pres vs. educ
p1 <- ggplot(cleaned_data, aes(x=educ, y=papres10)) +
  geom_point(color="#69b3a2", size=2,alpha=0.3) +
  ggtitle("Father's Prestige Score vs Children's Education") +
  labs(x="Education (in Years)", y="Father's Prestige Score")+
  theme_bw()
p2 <- ggplot(cleaned_data, aes(x=educ, y=mapres10)) +
  geom_point(color="darkgreen",size=2,alpha=0.3) +
  ggtitle("Mother's Prestige Score vs Children's Education") +
  labs(x="Education (in Years)", y="Mother's Prestige Score")+
  theme_bw()

@@

ggplot(cleaned_data, aes(x = educ, fill = factor(born))) +
  geom_histogram(position = "dodge", binwidth = 1.5, alpha = 0.5, color = "black")+
   labs(title = "Education and Birthplace (if outside of US) for the Respondent",
       x = "Education (in Years)",
       y = "Count",
       fill = "Birthplace of the Respondent (if in, of US)")+
  theme_bw()
```
```{r,echo=FALSE}
tb3 <- cleaned_data %>% 
  count(born) %>% 
  mutate(percent=percent(x=n/sum(n)))
```

@@

```{r,echo=FALSE}
tb4 <- cleaned_data %>% 
  count(reg16) %>% 
  mutate(percent=percent(x=n/sum(n)))
```

```{r}
#| label: fig-maincome
#| fig-cap: Education vs Mother's Education with respect to Family Income
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8
#| fig-height: 4
ggplot(cleaned_data, aes(x = educ, y = maeduc, color = incom16)) +
  geom_jitter(alpha = 0.2) +
  stat_smooth(method = "lm", se = FALSE) +
  facet_wrap(~incom16)+
  labs(title = "Education vs Mother's Education with respect to Family Income",
       x = "Education (in Years)",
       y = "Mother's Educaion (in Years)",
       color = "Family Income (at Age of 16)") +
  scale_color_discrete(name = "Family Income (at Age of 16)") +
  theme_bw()
```

@@

ggplot(cleaned_data, aes(x = educ, y = paeduc, color = incom16)) +
  geom_jitter(alpha = 0.2) +
  stat_smooth(method = "lm", se = FALSE) +
  facet_wrap(~incom16)+
  labs(title = "Education vs Father's Education with respect to Family Income",
       x = "Education (in Years)",
       y = "Father's Educaion (in Years)",
  color = "Family Income (at Age of 16)") +
  scale_color_discrete(name = "Family Income (at Age of 16)") +
  theme_bw()
```

@@

# Model {#sec-model}
